### 2021-02-23 input/figaddA.tex
coloring figures, adding biblio, sketching abstract
inter AS figure + lighter figures

\begin{tikzpicture}[scale=1]

@@

  \draw[fill=white] (0, 0) node{$\bm{a}$} +(-5, -5) rectangle +(5, 5);

>>>>

\begin{tikzpicture}[scale=0.87]

  \thickmuskip=0mu
  \medmuskip=0mu
  \thinmuskip=0mu

@@

  \newcommand\ADD{\alpha}

  \draw (-\X + 5pt, 0) -- (0 - 5pt, 0); %% a - b

  \draw (0 +5pt, 0) -- (\X -5pt, 0); %% b - c

  \draw (0, 0 - 5pt) -- (0, \Y + 5pt); %% d - b

  \draw (\X + 3pt, 0 - 5pt) -- (0 + 5pt, \Y - 3pt); %% c - d

  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0, \Y) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above, color=\PA]{$\ADD_a^0$};
  \draw (\X, 5pt) node[above, color=\PC]{$\ADD_c^0$};

### 2021-02-23 input/proposal.tex
inter AS figure + lighter figures

In this section, we introduce \NAME, (\TODO{stands for}) a reactive
protocol for logical partitioning in autonomous sytems the cost of
which actually depends on its usage: when the system becomes
quiescent, processes eventually converge to their respective partition
and do not require further communication afterwards.

@@

Autonomous systems are geo-distributed networks. Heterogenous
communication links. Hierarchy of communication links. Per-object
broadcast.

@@

>>>>

In this section, we introduce \NAME, (\TODO{stands for}) a reactive
protocol for logical partitioning in autonomous systems the cost of
which actually depends on its usage: when the system becomes
quiescent, processes eventually converge to their respective partition
and do not require further communication afterwards.

@@

\begin{figure}
  \centering\input{input/figAS.tex}
  \caption{\label{fig:AS}Inter autonomous systems partitioning. \TODO{new
      issue not introduced in background}}
\end{figure}

Autonomous systems are geo-distributed networks. Heterogeneous
communication links. Hierarchy of communication links. Per-object
broadcast.

@@

Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
where each process ranks its communication links, and each process
forwards messages to its neighbors starting from the rank of the link
that triggered the receipt, to its highest rank neighbors. In this
example, Process $e$ adds a partition. It forwards the generated
message to all its neighbors as if it received it from its lowest rank
links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
stops the propagation, for all its links have lower ranks than the one
from which it received the message $\alpha_e^2$. Ultimately, the
partition includes Process $e$, Process $a$, and Process $b$. Process
$c$ and Process $d$ remain unaware of the new \TODO{object}.
